\documentclass[11pt,letter,sans]{moderncv}

%% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{black}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}
\usepackage{amssymb}

%% Character encoding
\usepackage[utf8]{inputenc}
\usepackage{url}

%% Adjust the page margins
\usepackage[scale=0.88]{geometry}

%% Adjust the bullet-point style
%\renewcommand\labelitemi{\(^\cdot\)}


%% Personal data
\firstname{Chris}
\familyname{Cundy}


\mobile{016502509794}
\email{chris.j.cundy@gmail.com}
\social[github]{C-J-Cundy}
\extrainfo{Updated \today}

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Experience}
\cventry{June 2024--}{Research Scientist}{FAR.AI}
{Berkeley}{California, USA}{Characterising and mitigating catastrophic risks from frontier AI systems. My main responsibilities are:
  \begin{itemize}
  \item{Leading research projects and determining the direction for teams of researchers and engineers.}
  \item{Designing and implementing training and evaluation schemes with state-of-the-art models, conducting empirical studies, and communicating results through papers and presentations.}
  \item{As a research team lead, ensuring that research aims are consistent with FAR's mission and that my direct reports are supported in their output and professional development.}
  \end{itemize}}
\cventry{June 2022--September 2022}{Research Scientist Intern}{Technical AI Safety Team}
{DeepMind}{London, UK}{Investigating robust and reliable machine learning in theory and at scale
  \begin{itemize}
  \item{Investigated susceptibility of autoregressive models to `delusions', where unobserved latent variables lead to incorrect probabilistic judgments.}
  % \item{Developed a theoretical model for delusions and derived bounds on probabilistic error as a function of distribution shift.}
  \item{Developed a theoretical model for delusions; investigated delusions at scale by analysing performance of DeepMind's Gato (a large generalist, multi-task autoregressive model) on custom environments.}
  \end{itemize}}
\cventry{October 2017--January 2018}{Visiting Scholar}{Future of Humanity Institute}
{University of Oxford}{Oxford, UK}{Developing algorithms to predict
  human judgments. Supervised by Owain Evans and Andreas Stuhlm\"uller
  \begin{itemize}
  \item{Designed algorithms to collate quick, noisy human judgments to
      predict the answer to complicated tasks which would typically require deliberation.}
  \end{itemize}}
  \cventry{June--September 2017}{Visiting Scholar}
  {Centre for Human-Compatible AI}{University of California, Berkeley}
  {US}{Supervised by Daniel Filan \& Stuart Russell, researching topics in AI safety
    \begin{itemize}
    \item{Extended previous work on inverse reinforcement learning to hierarchical setting. Formalized
        the problem, derived theoretical results, performed experiments on
        data and presented at an ICML workshop.}
    \end{itemize}}


\section{Education}
\cventry{2018-2024}{PhD - Computer Science}{Stanford University}{Stanford, California}{USA}{
  \begin{itemize}
    \item{Advised by Stefano Ermon.}
    \item Investigating topics in inverse reinforcement learning, sequence modelling and variational inference.
    \item Thesis: \emph{Beyond Maximum Likelihood: Distribution-Aware Machine Learning}.
  \end{itemize}}
  

\cventry{2016-2017}{MEng - Computer Science}{University of Cambridge}{Cambridge}{UK}{
  \begin{itemize}
  \item{Grade: Distinction. Modules include: Data Science, Probabilistic Machine Learning,
      Network Analytics.}
    \item{Thesis: \emph{Investigating Variational Gaussian Process
          State-Space Models with Gaussian Likelihood}. \newline Supervised by Carl E. Rasmussen.}
    \end{itemize}}
  \cventry{2013-2016}{BA - Natural Sciences (Physics)}{University of Cambridge}
  {Cambridge}{UK} {
    \begin{itemize}
    \item{Grade: 1st. Modules: Physics, Maths, Chemistry, Computer Science.}
    \end{itemize}}

  % \cventry{2011--2013}{A Levels}{Simon Langton Grammar School for Boys}{Canterbury}
  % {UK}{Further Mathematics A*, Mathematics A*,
  %   Physics A*, Chemistry A*, History AS A}
  % \cventry{2006--2011}{GCSEs}{Simon Langton Grammar School for Boys}{Canterbury}
  % {UK}{10 A or A* including Mathematics and English}

  \section{Selected Publications}

  \cventry{2025}{Preference Learning with Lie Detectors can Induce Honesty or Evasion}
  {\newline \textbf{Chris Cundy}, Adam Gleave}{NeurIPS 2025}{}{}

  \cventry{2024}{SequenceMatch: Imitation Learning for Autoregressive Sequence Modelling with Backtracking}
  {\newline \textbf{Chris Cundy}, Stefano Ermon}{ ICLR 2024}{}{}

  \cventry{2024}{Privacy-Constrained Policies via Mutual Information Regularized Policy Gradients}
  {\newline \textbf{Chris Cundy}, Rishi Desai, Stefano Ermon}{ AISTATS 2024}{}{}  

  \cventry{2022}{LMPriors: Pre-Trained Language Models as Task-Specific Priors}
  {\newline Kristy Choi$^*$, \textbf{Chris Cundy}$^*$, Sanjari Srivasta, Stefano Ermon}{First Workshop on Foundation Models for Decision Making, NeurIPS 2022}{}{}
  

    \cventry{2021}{BCD Nets: Scalable Variational Approaches for Bayesian Causal Discovery}
    {\newline \textbf{Chris Cundy},  Aditya Grover, Stefano Ermon}{NeurIPS 2021}{}{}

    \cventry{2020}{Flexible Approximate Inference via Stratified Normalizing Flows}{\newline \textbf{Chris Cundy}, Stefano Ermon}{UAI 2020}{}{}

\cventry{2018}{Parallelizing Linear Recurrent Neural Nets over Sequence
  Length} {\newline Eric Martin, \textbf{Chris Cundy}}{ICLR 2018}{}{}    

\section{Additional Publications}
{ \small 
  \cventry{2025}{Sharpe Ratio-Guided Active Learning for Preference Optimization in RLHF}
  {\newline Syrine Belakaria, Joshua Kazdan, Charles Marx, \textbf{Chris Cundy}, Willie Neiswanger, Sanmi Koyejo, Barbara E Engelhardt, Stefano Ermon}{CoLM 2025}{}{}

  \cventry{2024}{A physics-informed machine learning model for the prediction of drop breakup in two-phase flows}
  {\newline \textbf{Chris Cundy}, Shahab Mirjalili, Charlélie Laurent, Stefano Ermon, Gianluca Iaccarino, Ali Mani}{International Journal of Multiphase Flow}{}{}

  \cventry{2023}{Neural Networks and the Chomsky Hierarchy}
  {\newline Gr\'{e}goire Del\'{e}tang, Anian Ruoss, Jordi Grau-Moya, Tim Genewein, Li Kevin Wenliang, Elliot Catt, \textbf{Chris Cundy}, Marcus Hutter, Shane Legg, Joel Veness, Pedro A. Ortega}{ICLR 2023}{}{}

  % \cventry{2023}{Beyond Bayes-optimality: meta-learning what you know you don't know}
  % {\newline Jordi Grau-Moya, Gr\'{e}goire Del\'{e}tang, Markus Kunesch, Tim Genewein, Elliot Catt, Kevin Li, Anian Ruoss, \textbf{Chris Cundy}, Joel Veness, Jane Wang, Marcus Hutter, Christopher Summerfield, Shane Legg, Pedro Ortega}{Technical Report}{}{}

    \cventry{2022}{Towards a foundation model for geospatial artificial intelligence}
  {\newline Gengchen Mai, \textbf{Chris Cundy}, Kristy Choi, Yingjie Hu, Ni Lao, Stefano Ermon}{Proceedings of the 30th International Conference on Advances in Geographic Information Systems}{}{}  

  \cventry{2021}{IQ-Learn: Inverse soft-Q Learning for Imitation}
  {\newline Divyansh Garg, Shuvam Chakraborty, \textbf{Chris Cundy}, Jiaming Song, Stefano Ermon}{NeurIPS 2021}{}{}

\cventry{2018}{Exploring Hierarchy-Aware Inverse Reinforcement Learning}
{\newline \textbf{Chris Cundy}, Daniel Filan}{Workshop on Goal Specifications for Reinforcement Learning, ICML 2018}{}{}

\cventry{2017}{Predicting Slow Judgment}{\newline Owain Evans, Andreas Stuhlm\"uller,
  Ryan Carey, Neal Jean, Andrew Schreiber, Girish Sastry, \textbf{Chris Cundy}}{Aligned Artificial Intelligence Workshop, NeurIPS 2017}{}{}

% \cventry{2015}{Simulation Of Plants In Buildings;
%   Incorporating Plant-Air Interactions In Building Energy Simulation}{\newline Rebecca Ward, Ruchi Choudhary, Christopher Cundy, George Johnson, Allan McRobie}
% {14th Conference of International Building Performance
%   Simulation Association}{}{}
% }

\section{Service}
\cventry{2025}{Participant, EU AI Act Code of Practice Working Groups 2 and 4}{}
{}{}{Participated, as an independent expert, in working groups 2 and 4 for the development of the EU AI Act Code of Practice (CoP).
  %The CoP is a set of detailed guidelines for how AI developers releasing in the EU can satisfy the AI Act of 2024.
  I advocated, via written and oral presentation, for the importance of pre- and post-mitigation model evaluations, outlined in an earlier position paper I authored. }
\cventry{2023}{Teaching Assistant--CS228 (Probabilistic Graphical Models)}{Stanford University}
{}{}{}
\cventry{2022}{Head Teaching Assistant--CS228 (Probabilistic Graphical Models)}{Stanford University}
{}{}{Received award for excellence (awarded to top 5\% of Teaching Assistants).}
\cventry{2023}{Project Supervisor}{Supervised Project for Alignment Research (SPAR)}
{Stanford AI Alignment}{}{Supervised five undergraduates on a project finding scaling laws in prompt injections.\newline Presented work at the 7th Center for Human-Compatible AI workshop.}
\cventry{2021}{Project Supervisor}{Undergraduate Research Program}
{Stanford Existential Risk Initiative}{}{Served as supervisor for an undergraduate project on forecasting AI progress.}
\cventry{2020--}{Reviewer}{}
{}{}{Reviewed for the following conferences: UAI (2020,2022,2025), ICML (2019,2020,2023,2025), ICLR (2021-2026), NeurIPS (2021-2025), AAAI-(Safe and Robust AI track) (2023-2024).}


\section{Relevant Awards}
\cventry{March 2024}{Winner, OpenAI Preparedness Challenge}{}{}{}{
  \begin{itemize}
  \item One of the top ten submissions for the OpenAI Preparedness Challenge, for submitting \emph{the most unique, while still being probable, potentially catastrophic misuse of the [OpenAI API]}.
  \item Developed proof-of-concept showing how GPT4-V, and speech-to-text with GPT4, could be used to parse vast amounts of unlabelled surveillance data, finding actionable insights for blackmail or insider trading.
  \item Prize: \$25,000 in OpenAI credits.
  \end{itemize}
}

% \cventry{June--August 2015}{Electricity Monitoring with C-AWARE}{Computer Lab,
% Cambridge University}{Cambridge}{UK}{Developing tools to measure electricity
% usage from remote sensors in university departments and present this
% data on the web
% \begin{itemize}
% \item{Conducted cost-benefit analysis to determine optimal appliance replacement
% timescales}
% \end{itemize} }

% \cventry{June--September 2014}{Computational Modelling of
% Greenhouses}{Engineering Department, Cambridge
% University}{Cambridge}{UK}{Developing methods to simulate heat flux in
% greenhouses
%   \begin{itemize}
%   \item{Designed and implemented a plugin to the popular building-simulation
% software, TRNSYS, incorporating plant-air interactions to building design.}
% \end{itemize} }

% \section{Non-Research Experience}
% \cventry{June--September 2016}{Research and Logistics Intern}{Local Effective
% Altruism Network}{Vancouver}{Canada}{Streamlining the administration workflow,
% analysing metrics and determining goals for a non-profit with a global reach
% \begin{itemize}
% \item{Conducted in-depth statistical analysis (using R) and produced a 30-page report summarizing a
%     2,500-strong survey of our users}
% \item{Used quantitative results to
% help define new goals for the organisation's upcoming year. }
% \item{Developed a bespoke system, using Google Scripts, Forms, and Streak, to
% manage customer relations and deliver timely replies to queries}
% \end{itemize}}


% \section{Prizes} \cventry{June 2017}{Sir Robert Cox Prize for Computer
% Science}{Christ's College}{Cambridge}{UK}{For a distinction in Computer
% Science.}

% \cventry{October 2016}{P.J. Fay Prize for Natural Sciences}{Christ's
% College}{Cambridge}{UK}{For first-class results in 2016 exams.}

% \cventry{October 2014 and 2015}{Grieg Prize for Natural Sciences}{Christ's
% College} {Cambridge}{UK} {For placing in the top 5 of 40 natural
% scientists at Christ's College, two years in a row.}{}{}

% \section{Selected Extracurricular Activities} \cvitem{Societies}{President of 80,000
% Hours: Cambridge, a university-wide society focusing on ethical careers, March
% 2016-17.\begin{itemize}
%   \item{ Ultimately responsible for overall strategy, increasing brand
% recognition through the 3,000-strong mailing list, and ensuring the year's
% events went smoothly: decided on concrete goals for the year and managed the
% committee of 12 people to fulfil these.}
%     \item{Events included interviews with television journalist Jon Snow, previous
% \emph{Guardian} editor-in-chief Alan Rusbridger, CEOs of multimillion-pound startups, as well as a series
% of careers workshops that have significantly changed the plans of over 70
% people.}
% \end{itemize}} 


\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
